Analysis of Fault Localization Techniques on REST APIs

### 2024-04-24 CS563-Project/Paper/paper.tex
Right now, working Git Miner is created and now, need to add the repos from the Paper, and then manually analyze the bugs, to make sure they are something that we can use

\subsection{Research questions}
    The primary research questions are formulated as follows:
    \begin{itemize}
        \item \textbf{RQ1:} Do fault localization techniques effectively localize faults in REST APIs?
        \item \textbf{RQ2:} What categories of faults (as per the existing taxonomy) are most effectively localized by current techniques?
        \item \textbf{RQ3:} Which fault localization techniques offer the highest accuracy and precision in the context of REST APIs?
    \end{itemize}
    \todo{What research question(s) will you answer?}

>>>>

\subsection{Research questions}
    The primary research questions are formulated as follows:
    \begin{itemize}
        \item \textbf{RQ1:} What categories of faults (as per the existing taxonomy) are most effectively localized by current techniques?
        \item \textbf{RQ2:} Which fault localization techniques offer the highest accuracy and precision in the context of REST APIs?
    \end{itemize}
    \todo{What research question(s) will you answer?}
